%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mussocv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Sam Musso}
\address{6436 Ammons St \linebreak Arvada CO 80004}
\contacts{(607) 794-0420 \linebreak sam.musso90@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Consulting Software Engineer}{Lunar Outpost}{Winter 2023}
			Stargate Mission Control (\textit{Languages: TypeScript, Python, Rust})			
			\begin{itemize}
				\item Designed and developed a fault tolerant ground station and Robotics as a Service Platform (Stargate).
				\item Stargate ensures delivery of both lunar \& terrestrial originated telemetry and reliable command dispatch.
				\item Stargate is built on AWS using a combination of serverless (Lambda) and containerized (K8s) microservices.
				\item Microfrontend architecture using ReactJS, GraphQL and REST.
				\item Built a navigational frontend (Atlas) to visualize the location of the lunar rover and its surroundings using streamed telemetry and in-situ landing photogrammetry. [CesiumJS, ArcGIS]
				\item Built a telemetry visualization \& command dispatch frontend (Pilot) for the lunar rover.
				\item All software will be critically in the loop for LO's 2024 mission deploying Nokia's lunar LTE network.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{L5 Software Engineer}{Amazon, Inc.}{Fall 2019 -- Winter 2023}
			Amazon.com (\textit{Languages: Java, Python, Kotlin, JavaScript, TypeScript})
			\begin{itemize}
				\item MicroServices development in Kotlin, Python, and Java on AWS with a focus on low DevOps overhead infra.
				\item Full-stack redesign of the cell phone trade-in workflow resulting in 100+\% increase in trade-ins.
				\item Designed and developed key portions of team's retail chat service yielding positive conversions.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Senior Software Engineer}{TAIT}{Spring 2017 -- Fall 2019}
			iQ And Navigator (\textit{Languages: C++, TypeScript, Python})
			\begin{itemize}
				\item Design and developed a Command \& Control UI (iQ) for the live entertainment industry, making live automation intuitive and accessible to a broader range of users.
				\item iQ leverages Qt and ReactJS to deliver a great looking \& high performance desktop application.
				\item iQ is now operational in venues like the Royal Opera House and NY Met Opera.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Alpine Labs}{Fall 2015 -- Spring 2017}
			Pulse Camera Controller	(\textit{Languages: C++, TypeScript, Python})
			\begin{itemize}
				\item Led firmware development in delivering Kickstarter's most funded photography gadget til then.
				\item Hybrid mobile app development for iOS / Android using Cordova, AngularJS, and Ionic.
				\item Delivered 65000+ units to 100+ countries with an engineering team of 4.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer in Test}{Netronome Systems, Inc.}{Feb 2014 -- Spring 2015}
			Network Flow Processing (\textit{Languages: C++, Python and C})
			\begin{itemize}
				\item QA new releases of our linux drivers, libraries, and utility apps for a suite of Network Accelerating ASICs.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer Co-op}{ANSYS, Inc.}{Spring 2011 -- Dec 2012}
			DesignModeler CAD (\textit{Languages: C++, Python})
			\begin{itemize}
				\item Software Development Intern on the DesignModeler team for ANSYS Workbench. 
				\item Improved the speed of the load and save operations by 800\% leveraging multi-processing (SMP).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Pittsburgh, PA}{University of Pittsburgh}{Fall 2009 -- Dec 2013}
			\begin{itemize}
				\item B.S.E. in Computer Engineering, Dec 2013.  In-major GPA: 3.4.
				\item Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item TypeScript; Python; C++; C; Java; Kotlin; SQL; JS; JSON; HTML; CSS; Bash;
				\item AWS; Docker; Kubernetes; Terraform; Jenkins; Git; Jira; Linux; MacOS; Windows;
				\item Scrum; Agile; TDD; BDD; CI/CD; Microservices; Serverless; REST; GraphQL;
				\item VS Code; Visual Studio; Eclipse; XCode; Vim; IntelliJ; Android Studio;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

